Applying Multi-Core Model Checking to Hardware-Software Partitioning in Embedded Systems

### 2015-08-16 Docs/Paper/LaTex/template.tex
Experimental Evaluation Edited

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[twocolumn]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%

\usepackage{booktabs}
\usepackage{tabu,xcolor,colortbl}
\usepackage{rotating}
\usepackage{amsmath,array}    
\usepackage[utf8]{inputenc} 
\DeclareUnicodeCharacter{FB01}{fi} %Caracter especial
\usepackage{graphicx} %Imagens
\usepackage{listings} % Codes
\usepackage{tabularx} % in the preamble
\usepackage{mathtools} % Serve para as equacoes

@@

Here, we exploit the availability of multi-core processors. In particular, a multi-core SMT-based BMC method is applied to the HW-SW partitioning and then is compared to the results with classical integer linear programming (ILP) and genetic algorithm (GA) using a multi-core tool as well. To the best of our knowledge, this is the first work to use a multi-core SMT-based verification to solve a HW-SW partitioning problem in embedded systems. We implement our ideas with the Efficient SMT-based Bounded Model Checker (ESBMC) tool [14]. As its main contribution, this paper shows that it is possible to take advantage of an SMT-based BMC tool in a multi-core architecture to solve optimization problems.

This paper is organized as follows: Section II gives a background on optimization, model checking, and multi-core support with Open MultiProcessing. Section III describes informal and formal mathematical modeling. Section IV describes briefly the binary integer programming and GA algorithms. The SMT-based BMC method is presented in Section V. Section VI presents the experimental evaluation. Section VII discusses related work. Section VIII presents the conclusion and future work.

@@

\subsection{Optimization with Vz}
Um solucionador SMT e uma ferramenta com finalidade de verificar a satisfabilidade de formulas baseada em um conjunto de regras SMT. Z3 e um solucionador SMT da Microsoft Research, disponibilizado livremente para a comunidade que integra suporte para uma variedade de teorias. Z3 tras consigo um solucionador DPLL juntamente de uma máquina de correspondencia para quantificadores. Z3 e implementado em C++.

vZ e uma das ferramentas implementadas no solucionador Z3, a funcao base desta ferramenta e otimizar objetivos dentro do contexto logico das restricoes, este se destaca pelas funcoes que dao a possibilidade de formular criterios de otimizacao. 
vZ inclui uma versao incremental de MaxRes para MaxSAT e um Simplex para solucionar numeros sem padrao definido, em seu nucleo MaxSat e responsavel pelas restricoes enquanto OptSMT tem como funcao otimizar objetivos de aritmetica linear.
Dentre todos os avancos do Z3 usando vZ destaca-se as funcoes: maximize, minimize and assert-soft.
\begin{itemize}
\item{\textbf{maximize(T)}
esta instrucao diz ao solucionador que a variavel T devera ser maximizada, e possível maximizar valores reais, inteiros e vetores de bit.}
\item{\textbf{minimize(T)}
esta instrucao diz ao solucionador que a variavel T devera ser minimizada, os tipos aceitos pelo minimize e similar ao maximize.}
\item{\textbf{Assert-Soft F :weight n}
a instrucao Assert-soft e uma restricao sobre F, e possível adicionar um peso n, o padrão e 1.} 
\end{itemize}

@@

Z3 is available for platforms like C, C ++, Java, .NET and Python, it is possible to download the Z3 with vZ in http://z3.codeplex.com. API in python was used to formulate the optimization problem on the vZ tool. The pseudo code below describes the steps to achieve desired results.

@@

\subsection{Multi-core ESBMC with OpenMP using Binary Search}
The original parallelization was made by continuously forking the instances of the ESBMC until the first violation is find.

@@

\section{Analysis of the partitioning problem using vZ}
O pseudocódigo abaixo mostra as condições aplicadas em ILP, GA e ESBMC convertida para a ferramenta vZ descrita em [34] e [35].

@@

\section{Experimental Evaluation}
ESBMC 1.24 running on a 64-bit Ubuntu 14.04.1 LTS operating system was used. Version 2.0.1 of Boolector SMT-solver [25] (freely available) was used as well. For the ILP and GA formulations, MATLAB R2013a from MathWorks with Parallel Computing Toolbox was used [18]. MATLAB is a dynamically typed high-level language known as the state-of-the-art mathematical software [19] and is widely used by the engineering community [20]. The ESBMC multi-core algorithm was implemented in C++1. A desktop with 24GB of RAM and i7 (8-cores) from Intel with clock of 3.40 GHz was used. Each time was measured 3 times in GA (average taken) and just once in ESBMC and ILP. The reason is that GA times are not so close as ESBMC and ILP. A time out condition (TO) is reached when the running time is longer than 7,200 seconds. A memory out (MO) occurs when the tool reaches 24GB of memory. TABLE I. lists the benchmarks1.

@@

The vertices in the graphs correspond to high-level language instructions. Software and communication costs are time dimensional, and hardware costs represent the occupied area.

The overall performance (TABLE II. ) shows that ILP is the best solution of all techniques, even if we consider that the Fuzzy benchmark reached time out with ILP. Thus, the maximum limit to use ILP is around 329 nodes or less. GA was the only technique that could solve all benchmarks, but the error from the exact solution varied from -37.6\% to 29\%.

Multi-core ESBMC had a better performance than that of pure ESBMC. The relative speedup obtained ranged from 1.9 to 60.3, which shows a reasonable improvement. Until the number of 150 nodes is reached, the ESBMC technique, mainly Multi-core ESBMC, has shown itself to be a good choice to solve HW-SW partitioning. This is because the exact solution was found and the execution time was mostly closer to ILP (from the same performance to 4.7 times faster). If the complexity of test vectors increases, then pure ESBMC algorithm has the drawback of creating an even more complex problem, because it increases the states created, which controls the hardware cost hint.

@@

With the RC6 benchmark (329 nodes), ESBMC was unable to present a solution without exceeding the time limit of 7200 seconds. Pure ESBMC had even a worse performance with Fuzzy and Mars, because the execution presented memory out. This is a clear indication that the prune method adopted by the ILP’s search tree solver is still more efficient than that adopted by ESBMC solver.

>>>>

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a general template file for the LaTeX package SVJour3
% for Springer journals.          Springer Heidelberg 2010/09/16
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % signs as needed.
%
% This template includes a few options for different layouts and
% content for various journals. Please consult a previous issue of
% your journal as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[twocolumn]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{booktabs}
\usepackage{tabu,xcolor,colortbl}
\usepackage{rotating}
\usepackage{amsmath,array}    
\usepackage[utf8]{inputenc} 
\DeclareUnicodeCharacter{FB01}{fi} %Caracter especial
\usepackage{graphicx} %Imagens
\usepackage{listings} % Codes
\usepackage{tabularx} % in the preamble
\usepackage{mathtools} % Serve para as equacoes

@@

\textcolor{Red}{Aqui, nós exploramos a disponibilidade de processadores multi-core, Em particular, são usados métodos baseados em SMT para analise do particionamento de HW-SW, em seguida, compara-se resultados usando PLI (programacao inteira linear), AG (Algoritmos Geneticos) em uma versão multicore, compara-se os resultados da ferramenta vZ da microsoft que se encontra no estado da arte[32], além de uma versão melhorada da busca em HW-SW para processadores multicores.} To the best of our knowledge, this is the first work to use a multi-core SMT-based verification to solve a HW-SW partitioning problem in embedded systems. We implement our ideas with the Efficient SMT-based Bounded Model Checker (ESBMC) tool [14]. As its main contribution, this paper shows that it is possible to take advantage of an SMT-based BMC tool in a multi-core architecture to solve optimization problems.

\textcolor{Red}{Este artigo está organizado da seguinte forma: a Seção 2 dá um fundo de otimização, otimizacao com a ferramenta vZ, utilizacao da técnica BMC com ESBMC, ESBMC com suporte a multiplos nucelos usando OpenMP, ESBMC Usando técnicas otimas de busca para multiplos nucleos com OpenMP. Seção 3 descreve a modelagem matemática informal e formal. Seção 4 descreve brevemente ILP e GA. O método BMC à base de SMT é apresentado na Seção 5. Seção 6 apresenta o modelo de particionamento usando o vZ. Seção 7 apresenta a avaliação experimental. Seção 8 discute os trabalhos relacionados. Seção 9 apresenta as conclusões e trabalhos futuros.}

@@

\subsection{\textcolor{Red}{Optimization with Vz}}
Um solucionador SMT e uma ferramenta com finalidade de verificar a satisfabilidade de formulas baseada em um conjunto de regras SMT. Z3 e um solucionador SMT da Microsoft Research, disponibilizado livremente para a comunidade que integra suporte para uma variedade de teorias. Z3 tras consigo um solucionador DPLL juntamente de uma máquina de correspondencia para quantificadores. Z3 e implementado em C++.
vZ e uma das ferramentas implementadas no solucionador Z3, a funcao base desta ferramenta e otimizar objetivos dentro do contexto logico das restricoes, este se destaca pelas funcoes que dao a possibilidade de formular criterios de otimizacao. 
vZ inclui uma versao incremental de MaxRes para MaxSAT e um Simplex para solucionar numeros sem padrao definido, em seu nucleo MaxSat e responsavel pelas restricoes enquanto OptSMT tem como funcao otimizar objetivos de aritmetica linear.
Dentre todos os avancos do Z3 usando vZ destaca-se as funcoes: maximize, minimize and assert-soft.

\begin{itemize}
\item{\textbf{maximize(T)}
esta instrucao diz ao solucionador que a variavel T devera ser maximizada, e possível maximizar valores reais, inteiros e vetores de bit.}
\item{\textbf{minimize(T)}
esta instrucao diz ao solucionador que a variavel T devera ser minimizada, os tipos aceitos pelo minimize e similar ao maximize.}
\item{\textbf{Assert-Soft F :weight n}
a instrucao Assert-soft e uma restricao sobre F, e possível adicionar um peso n, o padrão e 1.} 
\end{itemize}

@@

Z3 is available for platforms like C, C ++, Java, .NET and Python, it is possible to download the Z3 with vZ in http://z3.codeplex.com. API in python was used to formulate the optimization problem on the vZ tool.

@@

\subsection{\textcolor{Red}{Multi-core ESBMC with OpenMP using Binary Search}}
The original parallelization was made by continuously forking the instances of the ESBMC until the first violation is find.

@@

\section{\textcolor{Red}{Analysis of the partitioning problem using vZ}}
O pseudocódigo abaixo mostra as condições aplicadas em ILP, GA e ESBMC convertida para a ferramenta vZ descrita em [34] e [35].

@@

\section{Experimental Evaluation}
ESBMC 1.24 running on a 64-bit Ubuntu 14.04.1 LTS operating system was used. Version 2.0.1 of Boolector SMT-solver [25] (freely available) was used as well. For the ILP and GA formulations, MATLAB R2013a from MathWorks with Parallel Computing Toolbox was used [18]. MATLAB is a dynamically typed high-level language known as the state-of-the-art mathematical software [19] and is widely used by the engineering community [20]. \textcolor{Red}{A ferramenta vZ incorporada ao Z3[34] disponivel gratuitamente também foi usada. uma implementacao paralela do algoritmo ESBMC com busca sequencial ascendente, descrescente e binaria foi implementada em C++1}. A desktop with 24GB of RAM and i7 (8-cores) from Intel with clock of 3.40 GHz was used. Each time was measured 3 times in GA (average taken) and just once in ESBMC and ILP. The reason is that GA times are not so close as ESBMC and ILP. A time out condition (TO) is reached when the running time is longer than 7,200 seconds. A memory out (MO) occurs when the tool reaches 24GB of memory. TABLE I. lists the benchmarks1.

@@

\textcolor{Green}{The vertices in the graphs correspond to high-level language instructions. Software and communication costs are time dimensional, and hardware costs represent the occupied area.}  \textbf{Graphs nao deveria ser Tabela? acho que esse texto veio daquele artigo expandido. esse paragrafo faz sentido ao senhor? }

\textcolor{Red}{Os resultados obtidos destacam as ferramentas vZ e ILP.
Vz resolveu corretamente 4 de 7 algoritmos, teve um falso positivo no algoritmo RC6, seu resultado mais lento comparado a ILP Foi no algoritmo Patricia onde este foi 3.33 vezes mais rápido, vZ retornou dois TO(Time OUT) em Fuzzy e Mars.}

\textcolor{Red}{Em contrapartida, ILP Resolveu corretamente 6 de 7 algoritmos, não teve falso positivo, o tempo de resolucao do problema é maior quando comparamos com ILP/vZ e menor quando comparado com ILP/ESBMC, isso o coloca como uma ferramenta otima em resolucao e intermediaria no quesito tempo.  }

\textcolor{Red}{A unica tecnica capaz de resolver todos os benchmarks foi GA, entretanto, a precisão não foi satisfatoria, a taxa de erro variou entre -37.6\% até 29.0\%.}

\textcolor{Red}{Todas as versões do ESBMC paralelo obtiveram melhores resultados do que no modo sequencial, destaca-se a versão binaria descrita na secao 2.5, o desempenho se torna cada vez melhor quando se aumenta o numero de nós e arestas. o algoritmo Clustering quando processado pelo ESBMC paralelo obteve um desempenho 3.13 vezes melhor do que ILP, seu tempo de 207 segundos é muito proximo do tempo de solucao do Vz que é de 109 segundos. }

@@

\textcolor{Red}{A Tabela 2 mostra avancos na paralelizacao de algoritmos para problemas de particionamento, ESBMC obteve excelentes resultados quando executado de modo paralelo, as ferramentas vZ e ILP ainda se comportam de forma precisa frente ao ESBMC.}
